My title

### 2024-09-18 paper/paper.qmd
change read data

# Read data, https://stackoverflow.com/questions/78894145/quarto-document-not-seeing-project-directory-for-targets-data-functions-or-scr
raw_lead_data <- read_csv(here("data/raw/toronto_fire_incidents.csv"))
cleaned_data <- read_csv(here("data/analysis/cleaned_fire_data_simple.csv"))
```

>>>>

# Read data, https://stackoverflow.com/questions/78894145/quarto-document-not-seeing-project-directory-for-targets-data-functions-or-scr
raw_data <- read_csv(here("data/raw/toronto_fire_incidents.csv"))
cleaned_data <- read_csv(here("data/analysis/cleaned_fire_data_simple.csv"))
```
